Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2020-11-27 manuscript.tex
Merge branch 'master' of github.com:habi/zmk-tooth-cohort-method-manuscript [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/8fbce1cc53f2190b557d7a08e2ffe7c01c47e5f5.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/8fbce1cc53f2190b557d7a08e2ffe7c01c47e5f5/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/387341917

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...76040d57b99841c6ef4f59363df8779f86b9ddad}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/76040d57b99841c6ef4f59363df8779f86b9ddad/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/76040d57b99841c6ef4f59363df8779f86b9ddad}{habi/zmk-tooth-cohort-method-manuscript@76040d5}
on November 27, 2020.

@@

A total of 104 extracted human permanent mandibular canines were collected from university medical centers in southwest Germany and Switzerland.
All included teeth were extracted for reasons unrelated to the study and are so-called excess material making an institutional review board approval unnecessary for the purpose of this investigation.
The teeth were single-rooted and investigated according to their morphologic criteria.
Inclusion criteria for teeth selection were complete coronal and root development and the absence of root fracture and resorption, coronal and radicular caries and endodontic treatment.
Calculus as well as hard and soft tissue was removed using an ultrasonic scaler.
Afterwards, the teeth were placed for one hour in a 3\% hydrogen peroxide ultrasonic bath and then stored in 70\% ethanol {[}\protect\hyperlink{ref-1HkTk4VKM}{5}, \protect\hyperlink{ref-OttTicsv}{12}, \protect\hyperlink{ref-amSKhLb1}{15}, \protect\hyperlink{ref-ZTgDEakx}{17}, \protect\hyperlink{ref-1Gn1pVZXt}{19}{]}.

@@

The 104 human permanent mandibular canines in this study were collected from university medical centers in southwest Germany and Switzerland.
All included teeth were extracted for reasons unrelated to the study and are so-called excess material.
The teeth were used under irreversibly anonymized conditions and in accordance with the Swiss Human Research Law (\emph{Humanforschungsgesetz} {[}\protect\hyperlink{ref-4nfESi56}{37}{]}).
All donors were adults and gave written informed consent for research purposes.
This makes an ethics approval unnecessary for the purpose of this investigation.

@@

\leavevmode\hypertarget{ref-4nfESi56}{}%
37. SR 810.30 Bundesgesetz vom 30. September 2011 über die Forschung am Menschen (Humanforschungsgesetz, HFG). \url{https://www.admin.ch/opc/de/classified-compilation/20061313/index.html}. Accessed 27 Nov 2020.
\end{cslreferences}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...8fbce1cc53f2190b557d7a08e2ffe7c01c47e5f5}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/8fbce1cc53f2190b557d7a08e2ffe7c01c47e5f5/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/8fbce1cc53f2190b557d7a08e2ffe7c01c47e5f5}{habi/zmk-tooth-cohort-method-manuscript@8fbce1c}
on November 27, 2020.

@@

A total of 104 extracted human permanent mandibular canines were collected from university medical centers in southwest Germany and Switzerland.
All included teeth were extracted for reasons unrelated to the study and are so-called excess material.
The teeth were single-rooted and investigated according to their morphologic criteria.
Inclusion criteria for teeth selection were complete coronal and root development and the absence of root fracture and resorption, coronal and radicular caries and endodontic treatment.
Calculus as well as hard and soft tissue was removed using an ultrasonic scaler.
Afterwards, the teeth were placed for one hour in a 3\% hydrogen peroxide ultrasonic bath and then stored in 70\% ethanol {[}\protect\hyperlink{ref-1HkTk4VKM}{5}, \protect\hyperlink{ref-OttTicsv}{12}, \protect\hyperlink{ref-amSKhLb1}{15}, \protect\hyperlink{ref-ZTgDEakx}{17}, \protect\hyperlink{ref-1Gn1pVZXt}{19}{]}.

@@

The 104 human permanent mandibular canines in this study were collected from university medical centers in southwest Germany and Switzerland.
All included teeth were extracted for reasons unrelated to the study and are so-called excess material.
The teeth were used under irreversibly anonymized conditions and in accordance with the Federal Act on Research involving Human Beings (Human Research Act {[}\protect\hyperlink{ref-10OKzEtEb}{37}{]}).
All donors were adults and gave written informed consent for research purposes.
This makes an ethics approval unnecessary for the purpose of this investigation.

@@

\leavevmode\hypertarget{ref-10OKzEtEb}{}%
37. CC 810.30 Federal Act of 30 September 2011 on Research involving Human Beings (Human Research Act, HRA). \url{https://www.admin.ch/opc/en/classified-compilation/20061313/index.html}. Accessed 27 Nov 2020.
\end{cslreferences}
